Multi-target detection with application to cryo-electron microscopy

### 2019-03-03 inverse_problems/inverse_problems.tex
changing notation in Section 6.1

\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
\usepackage{verbatim}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{multirow}
\usepackage{color}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools} 
\usepackage{stackrel} 
%\usepackage[skip=1pt]{caption} % example skip set to 2pt

\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\SUM}{\text{sum}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\ii}{\textbf{i}}
\newcommand{\jj}{\textbf{j}}
\newcommand{\Poisson}{\text{Poisson}}
\newcommand{\II}{\mathcal{I}}
\newcommand{\kk}{\textbf{k}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\mb}{\mathbf}
\newcommand{\mk}{\mathfrak}
\newcommand{\mc}{\mathcal}
\newcommand*\Bell{\ensuremath{\boldsymbol\ell}}
\newcommand{\TODO}[1]{{\color{red}{[#1]}}}
\newcommand{\revised}[1]{{\color{blue}{#1}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\M}{\mathcal{M}}
\renewcommand{\P}{\mathbb{P}}
\renewcommand{\L}{\mathcal{L}}

%\newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
\makeatletter

@@

%\allowdisplaybreaks
\numberwithin{equation}{section}

@@

We consider the multi-target detection problem of recovering a set of signals that appear 
multiple times at unknown locations in a noisy measurement.
We derive simple relations between the autocorrelations of the observations and those of the signals. These autocorrelations can be estimate accurately in any noise level given sufficiently long measurement. 
To recover the signals from their autocorrelations, we suggest to solve a nonlinear least-squares. 
This is of particular importance in high noise regimes in which detecting individual signal appearance is impossible.
We provide rigorous analysis for the special case in which the same signal appears multiple times in the data, and demonstrate numerically the effectiveness of the method in a variety of settings.

The main goal of this work is to supply theoretical and numerical support for the possibility of estimating the 3-D structure of single particles using cryo-electron microscopy without detection~\cite{bendory2018toward}.

@@

Owing to the separation condition, when correlating $y$ with shifted versions of itself for shifts in $0, \ldots, L-1$, any given occurrence of $x$ in $y$ is only ever correlated with itself, and never with another occurrence. As a result, the autocorrelations of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the density $\gamma$ (which is a weak dependence on the support signal $s$). Specifically, we show the following identities in Section~\ref{sec:autocorrelation_computation}:
\begin{align} \label{eq:ac_well_separated}
	a_y^1 & = \gamma a_{x}^1, \nonumber \\
	a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell], \\
	a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\delta[\ell_1]+\delta[\ell_2]
	+\delta[\ell_1-\ell_2]\big), 
\end{align}
where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$, and indices $\ell, \ell_1, \ell_2$ are in the range $0 \leq \ell \leq L-1$. Terms proportional to $\sigma^2$ are due to the noise. If $\sigma$ is known, they can be handled easily. If $\sigma$ is unknown, one can either estimate it form the data, or one can ignore the few entries of the autocorrelations that are affected by $\sigma$---one in $a_y^2$ and $3L-2$ in $a_y^3$, a relatively small number in both cases.

We show in Section~\ref{sec:theory_homogeneous_well_separated} 
that $x,\gamma$ and $\sigma$ can be identified uniquely from the autocorrelations for the homogeneous case where $K = 1$ (all signal occurrences are the same).

@@

In Section~\ref{sec:proof_prop_poisson}, we prove the following expressions for the autocorrelations of $y$ under the Poisson model, expressed in terms of the autocorrelations of $x$ and the parameters $\gamma$ and $\sigma$:
%
\begin{align}
a_y^1  &=  \gamma a_{x}^1, 
\label{eq:mean_micrograph2} \\
a_y^2[\ell] &=  (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \delta[\ell], 
\label{eq:ac2_micrograph2} \\
a_y^3[\ell_1,\ell_2]  & = (\gamma a_x^1)^3 + \gamma a_x^1  
\cdot ( \gamma a_x^2[\ell_1] + \gamma a_x^2[\ell_2]
+ \gamma a_x^2[\ell_2-\ell_1]) + \gamma a_x^3[\ell_1,\ell_2] 
\nonumber \\
& \qquad + \gamma a_x^1 \sigma^2 \big(\delta[\ell_1]+\delta[\ell_2] +\delta[\ell_1-\ell_2] \big).
\label{eq:ac3_micrograph2}
\end{align}

In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify the signal $x$, the Poisson parameter $\gamma$ and the noise level $\sigma$ for generic $x$. 
%
%From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$. Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
%%
%\begin{align}
%\gamma a_x^3[\ell_1,\ell_2]
%= a_y^3[\ell_1,\ell_2] - (\gamma a_x^1)^3
%- \gamma a_x^1 \cdot \big(a_y^2[\ell_1]  
%+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(\gamma a_x^1)^2 \big).
%\end{align}

@@

For the Poisson model: 
From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$. Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
%
\begin{align}
\gamma a_x^3[\ell_1,\ell_2]
= a_y^3[\ell_1,\ell_2] - (a_y^1)^3
- a_y^1 \cdot \big(a_y^2[\ell_1]  
+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(a_y^1)^2 \big).
\end{align}

@@

Proofs for some of the results presented in Section~\ref{sec:AC_analysis} and~\ref{sec:extensions} follow in this section.

@@

%Let us define
%\begin{equation*}
%\gamma = \frac{|s|L}{N}>0.
%\end{equation*}
%Then the first order autocorrelation of the observation is given by 
%\begin{equation*}
%a_y^1 = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1} y[i]\right\} =
%\frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-1}x[i]\right\} +    
%\E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]\right\}
%=\gamma a_x^1,
%\end{equation*}
%where $\E_z$ means expectation with respect to the distribution of $z$.
%%the noise term converges to zero almost surely (a.s.)\ by the strong law of large numbers.
%
%We proceed with the second-order autocorrelation for  $\ell\in\{0,\ldots,L-1\}$. We can compute:
%%
%\begin{align*}
%%
%a_y^2[\ell] & = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]\right\}
%\nonumber \\
%& = \frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\right\}  + \E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell] \right\},
%%
%\end{align*}
%where all cross terms vanish in expectation owing to independence of $x$ of $\varepsilon$, and $\E{\varepsilon}=0$.  
%Hence, 
%\begin{align} \label{eq:2nd_moment_signal_term}
%%
%a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-1-\ell}{N}\sigma^2\delta[\ell],
%\end{align}
%where $\delta[0]=1$ and zero otherwise. 
%
%We now analyze the third-order autocorrelation. 
%Let $x_{(j)}$ denote the $j$th
%realization of $x$, with starting position $s_{(j)}$, for $j=1,\ldots,|s|$.
%Let us fix $0\leq \ell_2\leq\ell_1\leq L-1$. We have:
%\begin{align*}
%%
%a_y^3[\ell_1,\ell_2] 
%=& \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]\right\}
%\\
%%
%\stackrel{(1)}=& \E_{x_{(1)},\ldots,x_{(|s|)}}\left\{ \frac{|s|L}{N}\frac{1}{|s|}\sum_{j=1}^{|s|} 
%	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x_{(j)}[i]x_{(j)}[i+\ell_1]x_{(j)}[i+\ell_2]  \right\} \\
%\stackrel{(2)}+& \E_\varepsilon\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]\right\}
%\ \\
%\stackrel{(3)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\} \\
%\stackrel{(4)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_1]x_{(j)}[i]\ep[s_{(j)}+ i+\ell_2-\ell_1]\right\}
%\\
%\stackrel{(5)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_2]\ep[s_{(j)}+i+\ell_1-\ell_2]x_{(j)}[i]\right\}
%\\ \stackrel{(6)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_{(j)}+i-\ell_2]x_{(j)}[i+\ell_1-\ell_2]x_{(j)}[i]\right\}
%\\
%\stackrel{(7)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-\ell_2-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]x_{(j)}[i+\ell_2]\right\}
%\\ \stackrel{(8)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-\ell_1-1} x_{(j)}[i]x_{(j)}[i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\}.
%%
%\end{align*}
%Terms (6), (7) and (8) are linear in $\ep$ and  thus zero.
%Term (1) is equal  to $\gamma a_x^3[\ell_1,\ell_2]$  for the same reasons as~\eqref{eq:2nd_moment_signal_term}. 
%Term (2) is always zero by properties of Gaussian variables. 
%To deal with terms (3)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.
%
%Term (3) is always zero, unless $\ell_1=\ell_2$, so that it is equal to 
%$\gamma\sigma^2 a_x^1 \delta[\ell_1-\ell_2]$.
%The same goes for Terms (4) and (5), which are equal, respectively, to
%$\gamma\sigma^2 a_x^1 \delta[\ell_2]$ 
%and $\gamma\sigma^2 a_x^1 \delta[\ell_1]$.

@@

To address the second-order moments, we resort to the separation conditions. First, consider this expression:
\begin{align*}
N \cdot a_y^2[\ell] & = \E_y\left\{ \sum_{i = 0}^{N-\ell-1} y[i] y[i+\ell] \right\} \\
& = \sum_{i = 0}^{N-\ell-1} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\Bigg\{ \left( \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right) \cdot \\
& \qquad \qquad \qquad \qquad \qquad  \left( \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] + \varepsilon[i+\ell] \right)  \Bigg\} \\
& = \sum_{i = 0}^{N-\ell-1} \E_{x_{(1)}, \ldots, x_{(|s|), \varepsilon}}\Bigg\{ \sum_{j = 1}^{|s|} \sum_{j' = 1}^{|s|} I_{ij}  I_{i+\ell,j'} x_{(j)}[i-s_{(j)}]  x_{(j')}[i+\ell-s_{(j')}] \\
& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell] \\
& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] \varepsilon[i] \\
& \qquad \qquad \qquad \qquad \qquad \qquad + \varepsilon[i] \varepsilon[i + \ell] \Bigg\}.
\end{align*}
The cross-terms vanish in expectation since $\varepsilon$ is zero mean and independent from the signal occurrences. The last term vanishes in expectation unless $\ell = 0$ since distinct entries of $\varepsilon$ are independent. For $\ell = 0$, $\E\{\varepsilon[i]^2\} = \sigma^2$. Finally, using the separation property, observe that if $I_{ij}  I_{i+\ell,j'}$ is nonzero, then it is equal to one, $j = j'$ and $i = s_{(j)} + t$ for some $t$ in $0, \ldots, L-\ell-1$. Then, switch the order of summations to get
\begin{align}
N \cdot a_y^2[\ell] & = \sum_{j=1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-\ell-1} x_{(j)}[t] x_{(j)}[t+\ell] \right\} + (N-\ell)\sigma^2 \delta[\ell],
\end{align}
where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$. Since each $x_{(j)}$ is distributed as $x$, they all have the same autocorrelations as $x$ and we finally get
\begin{align}
a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-\ell}{N}\sigma^2 \delta[\ell] = \gamma a_x^2[\ell] + \sigma^2 \delta[\ell].
\end{align}

>>>>

\usepackage[T1]{fontenc}
\usepackage{verbatim}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools} 
\usepackage{stackrel}

\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\SUM}{\text{sum}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\ii}{\textbf{i}}
\newcommand{\jj}{\textbf{j}}
\newcommand{\Poisson}{\text{Poisson}}
\newcommand{\II}{\mathcal{I}}
\newcommand{\kk}{\textbf{k}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\mb}{\mathbf}
\newcommand{\mk}{\mathfrak}
\newcommand{\mc}{\mathcal}
\newcommand{\TODO}[1]{{\color{red}{[#1]}}}
\newcommand{\revised}[1]{{\color{blue}{#1}}}
\newcommand{\R}{\mathbb{R}}
%\newcommand{\M}{\mathcal{M}}
\newcommand{\M}{m}
\renewcommand{\P}{\mathbb{P}}
\renewcommand{\L}{\mathcal{L}}

\makeatletter

@@

\allowdisplaybreaks
\numberwithin{equation}{section}

@@

We consider the multi-target detection problem of recovering a set of signals that appear 
multiple times at unknown locations in a noisy measurement.
In the low noise regime, one can estimate the signals by first detect their occurrences and then cluster them.
In the high noise regime neither detection nor  clustering can be performed reliably and thus such a strategy is destined to fail.  
By employing autocorrelation analysis, we show that in some cases the signals themselves can be estimated  without detecting their occurrences. 
To estimate the signals, we derive simple relations between the autocorrelations of the observations and those of the signals. These autocorrelations can be estimate accurately in any noise level given sufficiently long measurement. 
To recover the signals from their autocorrelations, we suggest to solve a nonlinear least-squares. 
We provide rigorous analysis for the special case in which the same signal appears multiple times in the data, and demonstrate numerically the effectiveness of the method in a variety of settings.

The main goal of this work is to supply theoretical and numerical support for a recent suggestion to  estimate the 3-D structure of single particles using cryo-electron microscopy in extreme noise levels~\cite{bendory2018toward}.

@@

Owing to the separation condition, when correlating $y$ with shifted versions of itself for shifts in $0, \ldots, L-1$, any given occurrence of $x$ in $y$ is only ever correlated with itself, and never with another occurrence. As a result, the autocorrelations of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the density $\gamma$ (which is a weak dependence on the support signal $s$). Specifically, we show the following identities in Section~\ref{sec:autocorrelation_computation}:
\begin{align} 
	a_y^1 & = \gamma a_{x}^1, \label{eq:mean_micrograph} \\
	a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\ell[\ell], \label{eq:ac2_micrograph}\\
	a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\ell[\ell_1]+\ell[\ell_2]
	+\ell[\ell_1-\ell_2]\big), \label{eq:ac3_micrograph}
\end{align}
where $\ell[0] = 1$ and $\ell[\ell \neq 0] = 0$, and indices $\ell, \ell_1, \ell_2$ are in the range $0 \leq \ell \leq L-1$. Terms proportional to $\sigma^2$ are due to the noise. If $\sigma$ is known, they can be handled easily. If $\sigma$ is unknown, one can either estimate it form the data, or one can ignore the few entries of the autocorrelations that are affected by $\sigma$---one in $a_y^2$ and $3L-2$ in $a_y^3$, a relatively small number in both cases.

We show in Section~\ref{sec:theory_homogeneous_well_separated} 
that $x,\gamma$ and $\sigma$ can be identified uniquely from the observed autocorrelations for the homogeneous case where $K = 1$ (all signal occurrences are the same).

@@

In Section~\ref{sec:proof_prop_poisson}, we prove the following expressions for the autocorrelations of $y$ under the Poisson model. As in the well-separated model, the observed autocorrelations do not depend on individual occurrences of the signal, but only on $x$ itself, and the parameters $\gamma$ and $\sigma$:
%
\begin{align}
a_y^1  &=  \gamma a_{x}^1, 
\label{eq:mean_micrograph2} \\
a_y^2[\ell] &=  (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \ell[\ell], 
\label{eq:ac2_micrograph2} \\
a_y^3[\ell_1,\ell_2]  & = (\gamma a_x^1)^3 + \gamma a_x^1  
\cdot ( \gamma a_x^2[\ell_1] + \gamma a_x^2[\ell_2]
+ \gamma a_x^2[\ell_2-\ell_1]) + \gamma a_x^3[\ell_1,\ell_2] 
\nonumber \\
& \qquad + \gamma a_x^1 \sigma^2 \big(\ell[\ell_1]+\ell[\ell_2] +\ell[\ell_1-\ell_2] \big).
\label{eq:ac3_micrograph2}
\end{align}

In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify uniquely the signal $x$, the Poisson parameter $\gamma$ and the noise level $\sigma$ for generic $x$. 
%
%From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$. Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
%%
%\begin{align}
%\gamma a_x^3[\ell_1,\ell_2]
%= a_y^3[\ell_1,\ell_2] - (\gamma a_x^1)^3
%- \gamma a_x^1 \cdot \big(a_y^2[\ell_1]  
%+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(\gamma a_x^1)^2 \big).
%\end{align}

@@

For the Poisson model: 
From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$. Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
%
\begin{align}
\gamma a_x^3[\ell_1,\ell_2]
= a_y^3[\ell_1,\ell_2] - (a_y^1)^3
- a_y^1 \cdot \big(a_y^2[\ell_1]  
+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(a_y^1)^2 \big).
\end{align}

@@

%Proofs for some of the results presented in Section~\ref{sec:AC_analysis} and~\ref{sec:extensions} follow in this section.

@@

%Let us define
%\begin{equation*}
%\gamma = \frac{|s|L}{N}>0.
%\end{equation*}
%Then the first order autocorrelation of the observation is given by 
%\begin{equation*}
%a_y^1 = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1} y[i]\right\} =
%\frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-1}x[i]\right\} +    
%\E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]\right\}
%=\gamma a_x^1,
%\end{equation*}
%where $\E_z$ means expectation with respect to the distribution of $z$.
%%the noise term converges to zero almost surely (a.s.)\ by the strong law of large numbers.
%
%We proceed with the second-order autocorrelation for  $\ell\in\{0,\ldots,L-1\}$. We can compute:
%%
%\begin{align*}
%%
%a_y^2[\ell] & = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]\right\}
%\nonumber \\
%& = \frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\right\}  + \E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell] \right\},
%%
%\end{align*}
%where all cross terms vanish in expectation owing to independence of $x$ of $\varepsilon$, and $\E{\varepsilon}=0$.  
%Hence, 
%\begin{align} \label{eq:2nd_moment_signal_term}
%%
%a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-1-\ell}{N}\sigma^2\ell[\ell],
%\end{align}
%where $\ell[0]=1$ and zero otherwise. 
%
%We now analyze the third-order autocorrelation. 
%Let $x_{(j)}$ denote the $j$th
%realization of $x$, with starting position $s_{(j)}$, for $j=1,\ldots,|s|$.
%Let us fix $0\leq \ell_2\leq\ell_1\leq L-1$. We have:
%\begin{align*}
%%
%a_y^3[\ell_1,\ell_2] 
%=& \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]\right\}
%\\
%%
%\stackrel{(1)}=& \E_{x_{(1)},\ldots,x_{(|s|)}}\left\{ \frac{|s|L}{N}\frac{1}{|s|}\sum_{j=1}^{|s|} 
%	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x_{(j)}[i]x_{(j)}[i+\ell_1]x_{(j)}[i+\ell_2]  \right\} \\
%\stackrel{(2)}+& \E_\varepsilon\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]\right\}
%\ \\
%\stackrel{(3)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\} \\
%\stackrel{(4)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_1]x_{(j)}[i]\ep[s_{(j)}+ i+\ell_2-\ell_1]\right\}
%\\
%\stackrel{(5)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_2]\ep[s_{(j)}+i+\ell_1-\ell_2]x_{(j)}[i]\right\}
%\\ \stackrel{(6)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_{(j)}+i-\ell_2]x_{(j)}[i+\ell_1-\ell_2]x_{(j)}[i]\right\}
%\\
%\stackrel{(7)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-\ell_2-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]x_{(j)}[i+\ell_2]\right\}
%\\ \stackrel{(8)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
%	\sum_{i=0}^{L-\ell_1-1} x_{(j)}[i]x_{(j)}[i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\}.
%%
%\end{align*}
%Terms (6), (7) and (8) are linear in $\ep$ and  thus zero.
%Term (1) is equal  to $\gamma a_x^3[\ell_1,\ell_2]$  for the same reasons as~\eqref{eq:2nd_moment_signal_term}. 
%Term (2) is always zero by properties of Gaussian variables. 
%To deal with terms (3)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.
%
%Term (3) is always zero, unless $\ell_1=\ell_2$, so that it is equal to 
%$\gamma\sigma^2 a_x^1 \ell[\ell_1-\ell_2]$.
%The same goes for Terms (4) and (5), which are equal, respectively, to
%$\gamma\sigma^2 a_x^1 \ell[\ell_2]$ 
%and $\gamma\sigma^2 a_x^1 \ell[\ell_1]$.

@@

To address the second-order moments, we resort to the separation conditions. First, consider this expression:
\begin{align*}
N \cdot a_y^2[\ell] & = \E_y\left\{ \sum_{i = 0}^{N-\ell-1} y[i] y[i+\ell] \right\} \\
& = \sum_{i = 0}^{N-\ell-1} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\Bigg\{ \left( \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right) \cdot \\
& \qquad \qquad \qquad \qquad \qquad  \left( \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] + \varepsilon[i+\ell] \right)  \Bigg\} \\
& = \sum_{i = 0}^{N-\ell-1} \E_{x_{(1)}, \ldots, x_{(|s|), \varepsilon}}\Bigg\{ \sum_{j = 1}^{|s|} \sum_{j' = 1}^{|s|} I_{ij}  I_{i+\ell,j'} x_{(j)}[i-s_{(j)}]  x_{(j')}[i+\ell-s_{(j')}] \\
& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell] \\
& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] \varepsilon[i] \\
& \qquad \qquad \qquad \qquad \qquad \qquad + \varepsilon[i] \varepsilon[i + \ell] \Bigg\}.
\end{align*}
The cross-terms vanish in expectation since $\varepsilon$ is zero mean and independent from the signal occurrences. The last term vanishes in expectation unless $\ell = 0$ since distinct entries of $\varepsilon$ are independent. For $\ell = 0$, $\E\{\varepsilon[i]^2\} = \sigma^2$. Finally, using the separation property, observe that if $I_{ij}  I_{i+\ell,j'}$ is nonzero, then it is equal to one, $j = j'$ and $i = s_{(j)} + t$ for some $t$ in $0, \ldots, L-\ell-1$. Then, switch the order of summations to get
\begin{align}
N \cdot a_y^2[\ell] & = \sum_{j=1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-\ell-1} x_{(j)}[t] x_{(j)}[t+\ell] \right\} + (N-\ell)\sigma^2 \ell[\ell],
\end{align}
where $\ell[0] = 1$ and $\ell[\ell \neq 0] = 0$. Since each $x_{(j)}$ is distributed as $x$, they all have the same autocorrelations as $x$ and we finally get
\begin{align}
a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-\ell}{N}\sigma^2 \ell[\ell] = \gamma a_x^2[\ell] + \sigma^2 \ell[\ell].
\end{align}
